**The status of the microbial census: an update**

### 2015-12-05 results/tables/build_environmental_categories_table.Rmd
Shrink size so we don't need notitle.tex

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
    template: notitle.tex
tables: true
geometry: margin=1in
---

@@

coarse <- c("\\midrule\\multirow{2}{*}{Aerosol}",
			"\\midrule\\multirow{16}{*}{Aquatic}", "", "", "", "", "", "", "", "",
			"\\midrule\\multirow{11}{*}{Built}", "", "", "", "",
			"\\midrule\\multirow{6}{*}{Plant associated}", "", "",
			"\\midrule\\multirow{6}{*}{Soil}", "", "", "",
			"\\midrule\\multirow{6}{*}{Zoological}", "", "", "",
			"\\midrule\\multirow{2}{*}{Other}")

@@

composite <- xtable(text, caption=caption, label="")
align(composite) <- "lllp{10cm}"
print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1, nrow(composite)), comment=FALSE, add.to.row=addtorow, caption.placement = "top", size="footnotesize")
```

>>>>

---
output:
  pdf_document:
    includes:
      in_header: table_header.tex
tables: true
geometry: margin=1in
---

@@

coarse <- c("\\midrule\\multirow{1}{*}{Aerosol}",
			"\\midrule\\multirow{16}{*}{Aquatic}", "", "", "", "", "", "", "", "",
			"\\midrule\\multirow{10}{*}{Built}", "", "", "", "",
			"\\midrule\\multirow{5}{*}{Plant associated}", "", "",
			"\\midrule\\multirow{6}{*}{Soil}", "", "", "",
			"\\midrule\\multirow{6}{*}{Zoological}", "", "", "",
			"\\midrule\\multirow{1}{*}{Other}")

@@

composite <- xtable(text, caption=caption, label="")
align(composite) <- "lllp{10cm}"
print(composite, include.rownames=FALSE, include.colnames=TRUE, hline.after = c(-1, nrow(composite)), comment=FALSE, add.to.row=addtorow, caption.placement = "top", size="scriptsize")
```
